Constructing Sailing Match Race Schedules: Round Robin Pairing Lists

### 2015-03-24 paper.tex
Formatting for START etc

@@

\begin{flalign}
& f = \lceil n(n-1)/m  \rceil \label{eq1} \\
& t = n(n-1)/2 \label{eq2} \\
& \forall_{\tau \in [0..t-1]} ~ \timeSlot[{\tau}] \in \{-2..t-1\} \setminus \{\sigma\} \label{eq3} \\
& \forall_{i \in [0..f-1]} ~ \state[{i}] \in \{FIRST,MID,LAST,BYE,END\} \label{eq4} \\
& \forall_{i \in [0..f]} ~ \state[{i}] = FIRST \iff \timeSlot[{i \cdot m}] \geq 0  \label{eq5} \\
& \forall_{i \in [0..f]} ~ \state[{i}] = MID \iff  \exists_{j \in [i.m+1 ..  i.m+m-2]} ~ \timeSlot[{j}] \geq 0  \label{eq6} \\
& \forall_{i \in [0..f]} ~ \state[{i}] = LAST \iff \timeSlot[{(i+1).m - 1}] \geq 0  \label{eq7} \\
& \forall_{i \in [0..f]} ~ \state[{i}] = BYE \iff  \forall_{j \in [i.m ..  m.(i+1)-1]} ~ \timeSlot[j] = -1  \label{eq8} \\
& \forall_{i \in [0..f]} ~ \state[{i}] = END \iff  \forall_{j \in [i.m ..  m.(i+1)-1]} ~ \timeSlot[j] = -2  \label{eq9} \\
& \eachOccursExactlyOnce(\timeSlot, \{0, \ldots, n-1\} \setminus \{\sigma\}\})
\end{flalign}

@@

The constraints above are shown pictorially in Figure~\ref{skipper5}, and
corresponds to skipper 5 in the Table~\ref{tab1} schedule. The $\state$ array
is presented as coloured boxes, and below that is the $\timeSlot$ array. The
arrows represent the channeling constraints (\ref{eq5}) to (\ref{eq9}). The
$\state$ array is coloured with green representing LAST, yellow for MID, blue
for FIRST, red for LAST and (not shown) pink for BYE. The schedule of
Table~\ref{tab1} is reproduced with the matches for skipper 5 emboldened. To
the right of the schedule is schema for the DFA. Coloured arcs represent a
transition from one state to another. The DFA is encoded as a set of transition
objects $\langle q_{i},\iota,q_{j} \rangle$, where a transition is made from
state $q_{i}$ to state $q_{j}$ when encountering input $\iota$. In addition we
specify the accepting states, which are all states except the start state
(white) and the bye state (pink).

A boat change occurs when a skipper has been in a BYE state in flight $i$ and then is in a match in the next flight $i+1$. This is encoded using the array of zero/one variables (\ref{eq10}) and constraint (\ref{eq11}), and accumulated into $\totalChange$ (\ref{eq12}).

\begin{flalign}
    & \forall_{i \in [0..f-2]} ~ \change[{i}] \in \{0,1\} \label{eq10} \\
    & \forall_{i \in [0..f-2]} ~ \change[{i}] = 1 \iff \state[{i}] = BYE \wedge \state[{i+1}] \neq BYE \label{eq11} \\
    & \totalChange = \sum_{i=0}^{f-2} ~ \change[{i}] \label{eq12}
\end{flalign}

%\vspace{-6mm}
\begin{figure}[h]
\centering
\includegraphics[height=10.2cm,width=13.2cm]{skipper5.pdf}
\vspace{-25mm}
\caption{A pictorial representation of a skipper (skipper 5) with multicoloured state and grey timeslots. The schedule for skipper 5 is in bold and the deterministic finite automata for criteria 4, 11 and 12 is drawn with state START in white, FIRST in blue, MID in yellow, LAST in green, BYE in pink and END in red.}
\label{skipper5}
\end{figure}

>>>>

\newcommand{\START}{\textnormal{\textsc{Start}}}
\newcommand{\FIRST}{\textnormal{\textsc{First}}}
\newcommand{\MID}{\textnormal{\textsc{Mid}}}
\newcommand{\LAST}{\textnormal{\textsc{Last}}}
\newcommand{\END}{\textnormal{\textsc{End}}}
\newcommand{\BYE}{\textnormal{\textsc{Bye}}}

@@

\begin{flalign}
& f = \lceil n(n-1)/m  \rceil \label{eq1} \\
& t = n(n-1)/2 \label{eq2} \\
& \forall_{\tau \in [0..t-1]} ~ \timeSlot[{\tau}] \in \{-2..t-1\} \setminus \{\sigma\} \label{eq3} \\
& \forall_{i \in [0..f-1]} ~ \state[{i}] \in \{\FIRST,\MID,\LAST,\BYE,\END\} \label{eq4} \\
& \forall_{i \in [0..f]} ~ \state[{i}] = \FIRST \iff \timeSlot[{i \cdot m}] \geq 0  \label{eq5} \\
& \forall_{i \in [0..f]} ~ \state[{i}] = \MID \iff  \exists_{j \in [i.m+1 ..  i.m+m-2]} ~ \timeSlot[{j}] \geq 0  \label{eq6} \\
& \forall_{i \in [0..f]} ~ \state[{i}] = \LAST \iff \timeSlot[{(i+1).m - 1}] \geq 0  \label{eq7} \\
& \forall_{i \in [0..f]} ~ \state[{i}] = \BYE \iff  \forall_{j \in [i.m ..  m.(i+1)-1]} ~ \timeSlot[j] = -1  \label{eq8} \\
& \forall_{i \in [0..f]} ~ \state[{i}] = \END \iff  \forall_{j \in [i.m ..  m.(i+1)-1]} ~ \timeSlot[j] = -2  \label{eq9} \\
& \eachOccursExactlyOnce(\timeSlot, \{0, \ldots, n-1\} \setminus \{\sigma\}\})
\end{flalign}

@@

The constraints above are shown pictorially in Figure~\ref{skipper5}, and
corresponds to skipper 5 in the Table~\ref{tab1} schedule. The $\state$ array
is presented as coloured boxes, and below that is the $\timeSlot$ array. The
arrows represent the channeling constraints (\ref{eq5}) to (\ref{eq9}). The
$\state$ array is coloured with green representing $\LAST$, yellow for $\MID$, blue
for $\FIRST$, red for $\LAST$ and (not shown) pink for $\BYE$. The schedule of
Table~\ref{tab1} is reproduced with the matches for skipper 5 emboldened. To
the right of the schedule is schema for the DFA. Coloured arcs represent a
transition from one state to another. The DFA is encoded as a set of transition
objects $\langle q_{i},\iota,q_{j} \rangle$, where a transition is made from
state $q_{i}$ to state $q_{j}$ when encountering input $\iota$. In addition we
specify the accepting states, which are all states except the start state
(white) and the bye state (pink).

A boat change occurs when a skipper has been in a $\BYE$ state in flight $i$ and then is in a match in the next flight $i+1$. This is encoded using the array of zero/one variables (\ref{eq10}) and constraint (\ref{eq11}), and accumulated into $\totalChange$ (\ref{eq12}).

\begin{flalign}
    & \forall_{i \in [0..f-2]} ~ \change[{i}] \in \{0,1\} \label{eq10} \\
    & \forall_{i \in [0..f-2]} ~ \change[{i}] = 1 \iff \state[{i}] = \BYE \wedge \state[{i+1}] \neq \BYE \label{eq11} \\
    & \totalChange = \sum_{i=0}^{f-2} ~ \change[{i}] \label{eq12}
\end{flalign}

%\vspace{-6mm}
\begin{figure}[h]
\centering
\includegraphics[height=10.2cm,width=13.2cm]{skipper5.pdf}
\vspace{-25mm}
\caption{A pictorial representation of a skipper (skipper 5) with multicoloured state and grey timeslots. The schedule for skipper 5 is in bold and the deterministic finite automata for criteria 4, 11 and 12 is drawn with state $\START$ in white, $\FIRST$ in blue, $\MID$ in yellow, $\LAST$ in green, $\BYE$ in pink and $\END$ in red.}
\label{skipper5}
\end{figure}
